The Occurrence of Earth-Like Planets Around Other Stars

### 2014-11-26 paper/kepler-selection.tex
Changed abstract wording a bit (moved discussion of previous results to final paragraph).

\begin{abstract}
  The quantity $\etaearth$, the number density of planets per star per
  logarithmic planetary radius per logarithmic orbital period at one
  Earth radius and one year period, describes the occurrence of
  Earth-like extrasolar planets.  Measurement of $\etaearth$ is
  complicated by the difficulty of detecting Earth-like planets in
  Earth-like orbits about Sun-like stars.  Previous
  estimates\cite{Catanzarite2011,Traub2012,Dong2013,Petigura2013,Foreman-Mackey2014}
  place $1\% \lesssim \etaearth \lesssim 34\%$.  These works dealt
  with the problem of selection effects in the sample by either
  analysing a region of the period-radius parameter space where
  observations are complete and extrapolating to $R = \REarth$ and $P
  = 1 \mathrm{yr}$\cite{Catanzarite2011,Traub2012}, applying a binned
  analysis incorporating survey incompleteness in the period-radius
  plane\cite{Dong2013,Petigura2013} or analysing the results of a
  customised planet detection pipeline on a subset of the Kepler
  observations\cite{Petigura2013,Foreman-Mackey2014}.  Here we present
  a measurement of $\etaearth$ from a parameterised forward model of the
  (correlated) period-radius distribution and the observational
  selection function in the most recent (Q17) data release from the
  Kepler satellite\cite{Borucki2010,Borucki2011,Batalha2013}.  Our
  data set comprises 181,568 systems observed under the Kepler
  exoplanet observing program (mostly G-type stars on the main
  sequence\cite{Batalha2010}), producing 2598 planetary candidates.
  We parameterise the distribution of planetary periods and radii
  using a single, correlated Gaussian component; treat selection
  effects using a parameterised transit detection probability based on
  the measured noise level and stellar properties in the Kepler
  catalog; and include an empirically-parameterised, independent
  component in the period-radius distribution to represent
  false-positive planet detections.  Using our model we can
  simultaneously estimate $\etaearth$, place constraints on the planet
  period-radius distribution function, and determine the degree of
  contamination by false-positive candidate identifications.  We find
  $\etaearth = \earange$ (90\% CL).  We conclude that each
  star hosts $\rplrange$ planets with $P \lesssim 3 \mathrm{yr}$ and
  $R \gtrsim 0.2 \REarth$, that the peak of the planet radius
  distribution lies at $\Rpeak = \rpeakrange \REarth$, and that $\ln
  P$ and $\ln R$ are correlated with correlation coefficient $r =
  \corrcoeffrange$ (all 90\% CL).  Our empirical model for
  false-positive contamination is consistent with the dominant source
  being background eclipsing binary stars\cite{Fressin2013}, with
  $\fposrange$ (90\% CL) of the candidates being false-positives.  The
  distribution of planets we infer could be the result of a
  highly-stochastic planet formation process producing many correlated,
  fractional changes in planet sizes and orbits.  Our approach of
  determining both the intrinsic distribution of objects and selection
  effects empirically from survey data is generally applicable.
\end{abstract}

@@

The methods and analysed data sets of
Refs.\ \cite{Petigura2013,Foreman-Mackey2014} are most comparable to
ours.  These studies used the same data set,
produced\cite{Petigura2013} from a subset of the available Kepler data
and a customised pipeline to search for transit signals.  They both
accounted for selection effects by measuring the recoverability of
synthetic transit signals injected into their data, in contrast to our
approach of empirically determining them from the observed data.
Neither study attempted to account for contamination from
falsely-identified candidate transit events, controlling this instead
through careful choice of threshold.  Both studies used a more
flexible model for the intrinsic distribution of planets than ours.
Our result for $\etaearth$ is consistent with, but more precise than,
Ref.\ \cite{Foreman-Mackey2014} and (somewhat) inconsistent with
Ref.\ \cite{Petigura2013}.

>>>>

\begin{abstract}
  The quantity $\etaearth$, the number density of planets per star per
  logarithmic planetary radius per logarithmic orbital period at one
  Earth radius and one year period, describes the occurrence of
  Earth-like extrasolar planets.  Measurement of $\etaearth$ is
  complicated by the difficulty of detecting Earth-like planets in
  Earth-like orbits about Sun-like stars.  Here we present
  a measurement of $\etaearth$ from a parameterised forward model of
  the (correlated) period-radius distribution and the observational
  selection function in the most recent (Q17) data release from the
  Kepler satellite\cite{Borucki2010,Borucki2011,Batalha2013}.  Our
  data set comprises 181,568 systems observed under the Kepler
  exoplanet observing program (mostly G-type stars on the main
  sequence\cite{Batalha2010}), producing 2598 planetary candidates.
  We parameterise the distribution of planetary periods and radii
  using a single, correlated Gaussian component; treat selection
  effects using a parameterised transit detection probability based on
  the measured noise level and stellar properties in the Kepler
  catalog; and include an empirically-parameterised, independent
  component in the period-radius distribution to represent
  false-positive planet detections.  Using our model we can
  simultaneously estimate $\etaearth$, place constraints on the planet
  period-radius distribution function, and determine the degree of
  contamination by false-positive candidate identifications.  We find
  $\etaearth = \earange$ (90\% CL).  We conclude that each star hosts
  $\rplrange$ planets with $P \lesssim 3 \mathrm{yr}$ and $R \gtrsim
  0.2 \REarth$, that the peak of the planet radius distribution lies
  at $\Rpeak = \rpeakrange \REarth$, and that $\ln P$ and $\ln R$ are
  correlated with correlation coefficient $r = \corrcoeffrange$ (all
  90\% CL).  Our empirical model for false-positive contamination is
  consistent with the dominant source being background eclipsing
  binary stars\cite{Fressin2013}, with $\fposrange$ (90\% CL) of the
  candidates being false-positives.  The distribution of planets we
  infer is consistent with a highly-stochastic planet formation
  process producing many correlated, fractional changes in planet
  sizes and orbits.  Our approach of determining both the intrinsic
  distribution of objects and selection effects empirically from
  survey data is generally applicable.
\end{abstract}

@@

Previous
estimates\cite{Catanzarite2011,Traub2012,Dong2013,Petigura2013,Foreman-Mackey2014}
place $1\% \lesssim \etaearth \lesssim 34\%$.  These works dealt with
the problem of selection effects in the sample by either analysing a
region of the period-radius parameter space where observations are
complete and extrapolating to $R = \REarth$ and $P = 1
\mathrm{yr}$\cite{Catanzarite2011,Traub2012}, applying a binned
analysis incorporating survey incompleteness in the period-radius
plane\cite{Dong2013,Petigura2013} or analysing the results of a
customised planet detection pipeline on a subset of the Kepler
observations\cite{Petigura2013,Foreman-Mackey2014}.  The methods and
analysed data sets of Refs.\ \cite{Petigura2013,Foreman-Mackey2014}
are most comparable to ours.  These studies used the same data set,
produced\cite{Petigura2013} from a subset of the available Kepler data
and a customised pipeline to search for transit signals.  They both
accounted for selection effects by measuring the recoverability of
synthetic transit signals injected into their data, in contrast to our
approach of empirically determining them from the observed data.
Neither study attempted to account for contamination from
falsely-identified candidate transit events, controlling this instead
through careful choice of threshold.  Both studies used a more
flexible model for the intrinsic distribution of planets than ours.
Our result for $\etaearth$ is consistent with, but more precise than,
Ref.\ \cite{Foreman-Mackey2014} and (somewhat) inconsistent with
Ref.\ \cite{Petigura2013}.
